\begin{rubric}{Projects}
\entry*[Oct 2023 -- Nov 2023]%
	\textbf{Default Probability Prediction} (Course Project for Applied ML in Finance I)\\
	Preprocessed and performed exploratory data analysis on financial statement data of 200k Italian firms over 9 years with Python, Pandas, and Statsmodels.\\
	Selected features with Variance Inflation Factor (VIF) and developed an XGBoost-based Probability of Default model with variable-relation penalty and walk-forward validation, achieving 80\% ROC-AUC.\\
	Visualized results with Matplotlib and translated model outputs into a risk-adjustable strategy.

\entry*[Nov 2025 -- Dec 2025]%
	\textbf{Stronger Instrument for Causal Inference Between Maternal Smoking and Birth Outcomes} (Wharton Course Project, advised by Prof. Dylan Small)\\
	Designed a statistical study on the causal relationship between maternal smoking and birth outcomes using cigarette taxes as an instrumental variable (IV).\\
	Adapted IV strengthening to continuous IV, improving effective sample size $\hat{I}_{C}^{2}$ by 223\%.\\
	Built a reproducible Python workflow for data assembly, matching, diagnostics, and robustness checks.

\entry*[Nov 2025 -- Jan 2026]%
	\textbf{Hybrid Dirichlet Boundary Condition Enforcement in PINN} (Research Project at UPenn, advised by Prof. Paris Perdikaris)\\
	Investigated failure/success modes of Dirichlet BC enforcement in PINNs on 2D Stokes flow around a cylinder, comparing soft penalties and hard-constraint distance-filter ansatzes in JAX.\\
	Designed a hybrid hard--soft BC scheme that improved velocity-field accuracy by 66\% over baseline while identifying cylinder hard constraints as a source of high-frequency target amplification.

\entry*[Aug 2024 -- Dec 2024]%
	\textbf{A Game-Theoretic Approach to Personal Data Sharing} (Senior Capstone at NYU, advised by Prof. Mathieu Lauri\`ere and Prof. Hongyi Wen)\\
	Designed a game-theoretic model where users optimize personalization reward vs privacy risk while the platform controls aggregate privacy exposure.\\
	Derived Nash equilibrium and best-response dynamics, then implemented multi-agent time-series simulations in Python/Gymnasium with deep-RL policies.\\
	Learned strategies increased service personalization by 93\% over baseline while protecting privacy.

\entry*[Aug 2024 -- Jan 2025]%
	\textbf{Large Language Models for High School Math Problems with Prolog} (NYUSH research project, advised by Prof. Yik-Cheung Tam)\\
	Developed a self-supervised training algorithm enabling LLMs to solve math problems by generating Prolog programs without human-labeled traces.\\
	Trained Llama-3.1-8B reached GPT-4o-level accuracy (73\%) on MATH-500.
\end{rubric}
